\documentclass[10pt]{extarticle}
%\documentclass[]{file}
\usepackage[margin=0.2in]{geometry}
\usepackage{romannum}
\usepackage[most]{tcolorbox}
\usepackage{enumitem}
\usepackage{multicol}
\setlist[itemize]{noitemsep, topsep=0pt}
\addtolength{\parskip}{-1.5mm}
\tcbset{
    frame code={}
    center title,
    left=0pt,
    right=0pt,
    top=0pt,
    bottom=0pt,
    colback=gray!50,
    colframe=white,
    width=\dimexpr\textwidth\relax,
    enlarge left by=0mm,
    boxsep=3pt,
    arc=0pt,outer arc=0pt,
    }
\begin{document}
\begin{flushleft}
\noindent {\huge\textbf{Sourab Kumar}}
\end{flushleft}
3rd Year Undergraduate  \hfill\textbf{Email : }skumar5@mt.iitr.ac.in $|$ sourabyadav004@gmail.com
\\Department of Metallurgical and Materials Engineering \hfill\textbf{Phone : }+91-9410571484 $|$ +91-9100743286
\vspace{-6pt}
\\

\noindent\rule[0.5ex]{\linewidth}{1pt}
{\large \textbf{\begin{tcolorbox}\textsc{Areas of Interest}\end{tcolorbox}}}
\begin{itemize}
\item Data Analytics $|$ Product Management $|$ Business Development


\end{itemize}


{\large \textbf{\begin{tcolorbox}\textsc{Academic Qualifications}\end{tcolorbox}}}

\begin{center}
\begin{tabular}{|p{2.5cm}|p{6.0cm}|p{8.5cm}|p{1.8cm}|}
\hline
\centering{\textbf{Year}} & \centering{\textbf{Degree/Certificate}} & \centering{\textbf{Institute}} & \textbf{CGPA/$\%$}\\
\hline
\centering{2016} - Present & \centering{B.Tech} & \centering{Indian Institute of Technology, Roorkee} & 6.189/10\\
\hline
\centering{2016} & \centering{TSBSE(\Romannum{12})} & \centering{Narayana Junior College, Hyderabad} & 93.8$\%$\\
\hline
\centering{2014} & \centering{CBSE(\Romannum{10})} & \centering{Kendriya Vidyalaya, RK Puram 08, Delhi} & 10.00/10\\
\hline
\end{tabular}
\end{center}

\medskip
{\large \textbf{\begin{tcolorbox}\textsc{Internships}\end{tcolorbox}}}
\begin{itemize}
    \item \textbf{Yatra Online Pvt. Ltd.(yatra.com)} \hfill\hfill(\textit{May'19 - July'19})\\\textbf{Trainee}\textbf{}
\begin{itemize}
    \item Will be serving as an Intern Trainee with the organization during my upcoming Summer Internship.
\end{itemize}
\end{itemize}
\begin{itemize}
\item \textbf{Udaan.com (Hiveloop Technologies Pvt. Ltd.)} \hfill\hfill(\textit{May'18- July'18})\\\textbf{Market Development Intern}\textbf{} 
\begin{itemize}
\item Automated the Fleet on Street (FoS) tracking and ranking mechanism, based on various metrics, to obtain the data of visit efficiency based on multiple parameters using basic Data Analysis. 
\item  Assisted the FMCG team in listing sanitization \& brand management to improve product visibility on the application.
\item Lead the telecalling team to create a workflow and calling efficiency tracker by analyzing the previously available data.
\item Reduced the vehicle routing problem of last mile supply chain by analyzing previously available data. 
\item Worked on mapping of stores to identify probable areas to be targeted while aiming for the expansion of market base.
\end{itemize}
\end{itemize}
\vspace{-2mm}

\medskip
{\large \textbf{\begin{tcolorbox}\textsc{Projects}\end{tcolorbox}}}
\begin{itemize}
\item \textbf{Automobile Steel} \hfill\hfill(\textit{Jan'19- Present})\\\textbf{Mentor: }\textbf{Prof. B. K. Jha} $|$ Associate Faculty, Department of Metallurgical and Materials Engineering, IIT Roorkee
\begin{itemize}
\item Studied the innovations brought up in the automobile industry in terms of the body structures and strength of various parts. 
\item  Prepared a detailed report for a clear understanding for future references by the team during B. Tech. Project.
\end{itemize}
\end{itemize}
\begin{itemize}
\item \textbf{Case Study: Gender Diversity in Corporate world} \hfill\hfill(\textit{Jan'18-Apr'18})\\\textbf{Mentor: }\textbf{Prof. Rajib Lochan Dhar} $|$ Associate Professor, DoMS, IIT Roorkee
\begin{itemize}
\item Studied the story of \textbf{Dr. Reddys Laboratories} to understand the gender diversity and inclusion policies. 
\item  Submitted a report mentioning the importance of female inclusion and various probable ways to improve the gender ratio.
\end{itemize}
\end{itemize}
\vspace{-2mm}
%\medskip
%{\large \textbf{\begin{tcolorbox}\textsc{Other Projects}\end{tcolorbox}}}
%\begin{itemize}

%\end{itemize}
{\large \textbf{\begin{tcolorbox}\textsc{Awards/Scholarships/Academic Achievements}\end{tcolorbox}}}
\begin{itemize}
\item Received \textbf{Prime Minister Scholarship for Central Armed Police Forces and Assam Rifles} for Academic Year 2016-17.
\item Secured an \textbf{International Rank 206} in \textbf{15th SOF - National Science Olympiad} conducted in over 1000 cities in 14 Asian countries.
\item Secured a \textbf{School Rank 007} in \textbf{5th International Mathematics Olympiad} conducted during December 2011.
\item Received the \textbf{Certificate of Merit by KVS} and \textbf{Certificate of Excellence by Ashraya Hastha Trust(R)} for scoring a CGPA of 10.00 in class X.
\item Awarded with \textbf{Certificate of Achievement} for contribution as a Teaching Assistant for \textbf{HS 001A: Communication Skills - Basic} for a batch of Freshmen year students.
\end{itemize}


{\large \textbf{\begin{tcolorbox}\textsc{Skills/Softwares}\end{tcolorbox}}}
\begin{itemize}
\itemsep0em
\item \textbf{Computer Languages: }R $|$ Java $|$ C++ $|$ HTML $|$ SQL
\item \textbf{Software Packages: }R-3.5.1 $|$ Netbeans IDE $|$ Developer C++ $|$ MS Office $|$ Adobe Illustrator
\item \textbf{Languages Known: }English (SRW)$|$ Hindi (SRW) $|$ Telugu (SO)
\end{itemize}


{\large \textbf{\begin{tcolorbox}\textsc{Additional Online Courses and Relevant Academic Courses}\end{tcolorbox}}}
\begin{itemize}
\itemsep0em
\item \textbf{Data Analytics and Data Science: } The Analytics Edge (MITx 15.071x) $|$ Introduction to Data Science (DS101EN) 
\item \textbf{Coding and Software Development: } Codesdope C++ $|$ DEV276x: Learn to Program in Java $|$ Tutorialspoint.com: SQL
\item \textbf{Product Management: } Digital Product Management: Modern Fundamentals (Coursera) $|$  Product Design (Udacity)
\item \textbf{Economics and Management: } Strategic Human Resource Management (IBM-304) $|$ Economics (HSS -01) $|$ Environmental Economics (IHS-323) $|$ Marketing Analytics: Competitive Analysis and Market Segmentation (BerkeleyX-BUSADM466.3x)
\item \textbf{Mathematics: } Probabilistic System Analysis and Applied Probability(MIT OCW 6.041 $|$ Mathematics (MAN-001)
\item \textbf{Finance: } Learn and Master the Basics of Finance(Udemy)
\end{itemize}


\medskip
{\large \textbf{\begin{tcolorbox}\textsc{Positions of Responsibility and Extra Curriculars}\end{tcolorbox}}}
\begin{itemize}
\item \textbf{Academic Reinforcement Program, IIT Roorkee}\hfill\hfill(\textit{November 2017-Present})
\begin{itemize}
\item \textbf{Section Head, Design: }July 2018-Present $|$ \textbf{Executive: }November 2017-April 2018
\item Supervised the design team to ensure improvement in the online and on-campus presence of the group.
\item Facilitating the knowledge exchange between freshmen and senior year students by multiple means.
\item Facilitated multiple open sessions and non-academic professionally relevant courses for the interested students.
\end{itemize}
\item \textbf{National Service Scheme, IIT Roorkee}\hfill\hfill(\textit{August 2016-Present})
\begin{itemize}
\item \textbf{Cell Secretary, Design: }July 2018-Present $|$ \textbf{Executive, Editorial and Photography Cell: }July 2017-April 2018 $|$ \textbf{Volunteer: }August 2016-April 2017
\item Mentored editorial and design team to ensure literary outreach and promotion of various events organized around the year.
\item Working for socially underprivileged people of society in multiple direct and indirect manners.
\end{itemize}
\item \textbf{National Social Summit 2018, IIT Roorkee}\hfill\hfill(\textit{November 2017-April 2018})
\begin{itemize}
\item \textbf{Manager, Events and Design: }November 2017-April 2018
\item Mentored design team members to ensure on-campus and off-campus promotions of various Summit events.
\item Organized the first social fest under the banner of NSS to bring numerous social groups \& NGOs on a single platform.
\end{itemize}
\item \textbf{SPIC MACAY IIT Roorkee Chapter}\hfill\hfill(\textit{September 2016-Present})
\begin{itemize}
\item \textbf{Volunteer and Content Writer: } July 2018-Present $|$ \textbf{Volunteer: }September 2016-April2018
\item Guided the editorial and design team to ensure literary outreach and promotion of various events organized around the year
\item Promoting the Indian culture among the college students by organizing multiple events during the academic year.
\end{itemize}
\item \textbf{Thomso IIT Roorkee}\hfill\hfill(\textit{September 2016-October 2016})
\begin{itemize}
\item \textbf{Event Coordinator: } September 2016-October 2016
\item Coordinated Guest Talks of various eminent personalities during the fest, namely Major Gaurav Arya, Ayaz Memon, etc.
\item Co-authored social media content and organized guest talks of various renowned personalities.
\end{itemize}

\item \textbf{Prama Jyoti Foundation}\hfill\hfill(\textit{September 2018-Present})
\begin{itemize}
\item \textbf{Volunteer: } September 2018-Present
\item Successfully organized the Micro-fiction writing competition in association with National Social Summit 2019.
\item Assisted the team in organizing the Celebrating Life Awards 2019 in student fraternity promotions and response collection.
\item Co-authored social media content and organized guest talks of various renowned personalities.
\end{itemize}

\vspace{1mm}
\end{itemize}
%\medskip
%\newpage
%\end{itemize}
{\large \textbf{\begin{tcolorbox}\textsc{Extra-Curricular Activities}\end{tcolorbox}}}
\begin{itemize}
\item Participated in the \textbf{CASE STUDY Challenge SMOG} during \textbf{Cognizance 2018}.
\item Runner up of \textbf{CASE STUDY Challenge on TechEd} held during \textbf{National Social Summit 2019}.
\item Participated in the \textbf{Intra-Regional Level} of \textbf{20th National Child Science Congress} organized on theme of \textbf{ENERGY: Explore, Harness and Conserve} during 2012-13.
\item Participated in the \textbf{GREEN Olympiad 2010} organized by the Ministry of Environment and Forests, Government of India.
\end{itemize}
\end{document}
